\begin{vita}
\vspace{-20pt}
\dateitem{May 2011}{B.S., B.A. University of Kansas, Lawrence, Kansas, USA}
\dateitem{September 2011 -- May 2013}{Graduate Teaching Assistant, Ohio State University, Columbus, Ohio, USA}
\dateitem{August 2013}{M.Sc. Ohio State University, Columbus, Ohio, USA}
\dateitem{September 2013 -- August 2017}{Graduate Research Assistant, Ohio State University, Columbus, Ohio, USA}

%\dateitem{February 31, 1969}{Born---Crazytown, OH}
%\dateitem{Mayuary, 2000}{B.S., Party College, Party Town, Party State}
% Insert other relevant items here (GTA, etc.)

\begin{publist}
\pubitem{``Search for Higgs boson pair production in the \bbWW final state at $\sqrt{s}=13$ TeV the ATLAS detector'', with M. Aaboud et. al. [ATLAS Collaboration], In preparation}
\pubitem{``Measurement of the $W$ Boson Helicity Fractions in \ttbar Events at $\sqrt{s}=8$ TeV in the Lepton + Jets Channel with ATLAS'', with M. Aaboud et. al. [ATLAS Collaboration], Eur. Phys. J. C 77 (2017) 264}
\pubitem{``Measurements of $Z\gamma$ electroweak production in association with a high-mass dijet system at $\sqrt{s}=$ 8 TeV with the ATLAS detector'', with M. Aaboud et. al. [ATLAS Collaboration], Submitted to Journal of High Energy Physics}
\pubitem{``Search for Higgs boson decays to a photon and a $Z$ boson in $pp$ collisions at $\sqrt{s}=$ 7 and 8 TeV with the ATLAS detector'', with M. Aaboud et. al. [ATLAS Collaboration], Phys. Lett. B, 732, 8 (2014)}
%\pubitem{Paper 1}
%\pubitem{Paper 2}
\end{publist}

\begin{fieldsstudy}
\vspace{-10pt}
\majorfield{Physics}
\onestudy{LHC physics, higgs decays, top quark physics, di-higgs searches, $t\bar{t}$ measurements, statistical interpretations of data, hardware and software development} % optional
% Alternatively you can do:
% \begin{studieslist}
% \studyitem{Topic 1}{Professor 1}
% \studyitem{Topic 2}{Professor 2}
% \studyitem{Topic 3}{Professor 3}
% \end{studieslist}
\end{fieldsstudy}

\end{vita}
