\section{Systematic uncertainties}
\label{sec:syst}
This section describes the sources of systematic uncertainties considered in the analysis. These uncertainties are divided into three categories: experimental uncertainties, uncertainties on the modeling of background processes estimated from simulation, and theoretical uncertainties on the signal processes. Each systematic uncertainty is treated as a nuisance parameter in the statistical fit. These systematic variations are estimated on the final expected yield in the signal regions.

\subsection{Experimental uncertainties}

Each reconstructed object has several sources of uncertainties, each of which are evaluated separately. The leading instrumental uncertainties are the uncertainty on the $b$-tagging efficiency and the jet energy scale (JES). The summary of experimental uncertainties is presented in Table~\ref{tab:syst_summary_sources}.
 
 \begin{table}[h]
\centering
\small
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Source        & Description                          & Analysis Name                         \\ 
\hline
%Muons         & Trigger                                 &    Muons\_Trig                              \\
Muons         & \pt resolution MS                 &   MUON\_MS                           \\ 
Muons         & \pt resolution ID                   &   MUON\_ID                             \\ 
Muons         & \pt scale                               &   MUON\_SCALE                     \\ 
Muons         & Isolation efficiency SF         &   MUON\_ISO\_SYS               \\ 
Muons         & Isolation efficiency SF         &   MUON\_ISO\_STAT              \\ 
Muons         & Reconstruction efficiency SF         &  MUON\_EFF\_SYS             \\ 
Muons         & Reconstruction efficiency SF         &  MUON\_EFF\_STAT           \\ 
Muons         & Trigger efficiency SF            &  MUON\_EFF\_TrigStatUncertainty \\ 
Muons         & Trigger efficiency SF            &  MUON\_EFF\_TrigSystUncertainty  \\ 
%Muons         & TTVA efficiency SF         &   MUON\_TTVA\_SYS              & \\ 
%Muons         & TTVA efficiency SF         &   MUON\_TTVA\_STAT             & \\ 
\hline
Electrons         & \pt resolution                           &   EG\_RESOLUTION\_ALL       \\ 
Electrons         & \pt scale                                  &   EG\_SCALE\_ALL                   \\ 
Electrons         & Isolation efficiency SF             &   EL\_EFF\_Iso\_TOTAL\_1NPCOR\_PLUS\_UNCOR  \\ 
Electrons         & Reconstruction efficiency SF  &   EL\_EFF\_Reco\_TOTAL\_1NPCOR\_PLUS\_UNCOR  \\ 
Electrons         & Trigger efficiency SF               &   EL\_EFF\_Trigger\_TOTAL\_1NPCOR\_PLUS\_UNCOR  \\ 
Electrons         & Identification efficiency SF      &   EL\_EFF\_ID\_TOTAL\_1NPCOR\_PLUS\_UNCOR  \\ 
\hline
MET           & Soft term                       &   MET\_SoftTrk\_ResoPerp            \\ 
MET           & Soft term                       &   MET\_SoftTrk\_ResoPara            \\ 
MET           & Soft term                       &   MET\_SoftTrk\_Scale              \\ 
\hline
Small-R Jets  & JES strongly reduced            &   JET\_SR1\_JET\_GroupedNP\_1                   \\ 
Small-R Jets  & JES strongly reduced            &   JET\_SR1\_JET\_GroupedNP\_2                   \\ 
Small-R Jets  & JES strongly reduced            &   JET\_SR1\_JET\_GroupedNP\_3                   \\ 
Small-R Jets  & JES strongly reduced            &   JET\_SR1\_JET\_EtaIntercalibration\_NonClosure  \\ 
Small-R Jets  & Energy resolution                  &   JET\_JER\_SINGLE\_NP                               \\ 
Small-R Jets  & JVT efficiency SF                  &   JET\_JvtEfficiency                                                   \\ 
\hline
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_0                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_1                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_2                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_3                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_4                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_5                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_6                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_7                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_8                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_9                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_10                             \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_11                             \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_12                             \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light\_13                             \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_B\_0                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_B\_1                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_B\_2                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_B\_3                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_B\_4                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C\_0                              \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C\_1                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C\_2                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C\_3                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C\_4                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_extrapolation                           \\
$b$-tagging     & Flavor tagging scale factors    &   FT\_EFF\_Eigen\_extrapolation\_from\_charm     \\
\hline
\hline
\end{tabular}
\caption{ Qualitative summary of the object systematic uncertainties included in this analysis. }
\label{tab:syst_summary_sources}
\end{center}
\end{table}

 
 
 \iffalse
\begin{table}[h]
\centering
\small
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Source        & Description                     & Analysis Name
  \\ \hline
Muons          & Trigger      & Muons\_Trig \\
Muons         & \pt resolution MS               &   MUONS\_MS                          \\ 
Muons         & \pt resolution ID               &   MUONS\_ID                           \\ 
Muons         & \pt scale                       &   MUONS\_SCALE                        \\ 
Muons         & Isolation efficiency SF         &   MUON\_ISO\_SYS                      \\ 
Muons         & Isolation efficiency SF         &   MUON\_ISO\_STAT                     \\ 
Muons         & Identification efficiency SF    &   MUON\_EFF\_SYS                      \\ 
Muons         & Identification efficiency SF    &   MUON\_EFF\_STAT                     \\ \hline
MET           & Soft term                       &   MET\_SoftTrk\_ResoPerp              \\ 
MET           & Soft term                       &   MET\_SoftTrk\_ResoPara              \\ 
MET           & Soft term                       &   MET\_SoftTrk\_ScaleUp               \\ \hline
Small-R Jets  & JES strongly reduced            &   JET\_GroupedNP\_1                   \\ 
Small-R Jets  & JES strongly reduced            &   JET\_GroupedNP\_2                   \\ 
Small-R Jets  & JES strongly reduced            &   JET\_GroupedNP\_3                   \\ 
Small-R Jets  & Energy resolution               &   JET\_JER\_SINGLE\_NP                \\ \hline
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light0                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light1                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light2                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light3                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_Light4                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_B0                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_B1                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_B2                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C0                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C1                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C2                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_C3                               \\
$b$-tagging     & Flavor tagging scale factors    &    FT\_EFF\_Eigen\_extrapolation                               \\
$b$-tagging     & Flavor tagging scale factors    &   FT\_EFF\_Eigen\_extrapolation\_from\_charm                               \\
\hline
Modeling      & $t\bar{t}$ ME              & Matching &       TopMCaNLOtt    \\ 
Modeling      & $t\bar{t}$ Scale             &      ScaleVariation  & Top\_Scale      \\ 
Modeling      & $t\bar{t}$ PDF             &    PDFVariation &    Top\_PDF     \\ 
Modeling      & $t\bar{t}$ PS               & Parton Shower &       Top\_PS    \\ 
\hline
\end{tabular}
\caption{ Qualitative summary of the systematic uncertainties included in this analysis. }
\label{tab:syst_summary_sources}
\end{center}
\end{table}
\fi

\clearpage

\subsubsection{Luminosity}
The uncertainty in the combined 2015+2016 integrated luminosity is calculated to be 3.2\%. %\footnote{\url{https://twiki.cern.ch/twiki/bin/view/Atlas/LuminosityForPhysics}}. 
It is derived from a preliminary calibration of the luminosity scale using x-y beam-separation scans performed in August 2015 and May 2016~\cite{Aaboud:2016hhf}. The luminosity uncertainty is applied to those backgrounds estimated from simulation and the signal samples.

\subsubsection{Trigger}
Systematic uncertainties on the efficiency of electron and muon triggers are evaluated as recommended by the corresponding ATLAS combined performance groups.% as documented here.\footnote{el: \url{https://twiki.cern.ch/twiki/bin/viewauth/AtlasProtected/ElectronEfficiencyRun2} \\ mu:\url{https://twiki.cern.ch/twiki/bin/view/AtlasProtected/MCPAnalysisGuidelinesMC15}} 

\subsubsection{Muons}
The following systematic uncertainties are applied to muons in estimations based on the simulation:

\begin{itemize}
\item Identification efficiency: The efficiencies are measured with the tag and probe method using the $Z$ mass peak.
\item Energy and Momentum scales: These are also measured with $Z$ mass line shape, and provided by the CP groups. 
\end{itemize}

\subsubsection{Electrons}

The following systematic uncertainties are applied to electron in estimations based on the simulation:

\begin{itemize}
\item Identification efficiency: The efficiencies are measured with the tag and probe method using the $Z$ mass peak.
\item Energy and Momentum scales: These are also measured with $Z$ mass line shape, and provided by the CP groups. 
\end{itemize}

\subsubsection{Jet uncertainties}
The jet energy uncertainties are derived based on in situ measurements performed during Run1 and from MC simulation extrapolations from Run1 to Run2 conditions ~~\cite{ATL-PHYS-PUB-2015-015}. The jet energy resolution uncertainty is evaluated by smearing jet energies according to the systematic uncertainties of the resolution measurement~~\cite{Aad:2014bia}. The uncertainty in the $b$-tagging efficiency is evaluated by propagating the systematic uncertainty in the measured tagging efficiency for $b$-jets~~\cite{ATLAS-CONF-2014-004}. 

\subsubsection{Missing transverse energy}
The systematic uncertainties related to the missing transverse energy are obtained by the propagation of the systematic uncertainty on the objects that build the MET, in particular the muon, electron and jets energy resolution and scale. The resolution and scale of the MET soft-term is broken down into its components: METScale, METResoPara, METResoPerp, and full uncertainties from each component is taken into account in the final fit. 
 
\subsection{Background modeling uncertainties}
Several systematics have been evaluated to take into account the uncertainties on the modeling of backgrounds. 

\subsubsection{Uncertainties from the modeling of $t\bar{t}$}
\label{sec:topsys}
The dominant background $t\bar{t}$ is normalized in CR1 for the low
mass selection and in CR2 for the high mass selection. MC is used to extrapolate the shapes from the control regions to the signal region, so theoretical uncertainties are related to such extrapolation. PDF and scale uncertainties are evaluated by applying event selection at truth level. The resulting uncertainties are approximately 4\% and included in the final fit.  

Additional uncertainties in $t\bar{t}$ modeling stems from the difference in the matrix element (ME) implementation across generators, hadronization and fragmentation modeling (called parton shower, PS), and the amount of initial and final state radiation (ISR/FSR). The ME uncertainty is computed by comparing the events generated by \textsc{aMC@NLO} with the events generated by \textsc{Powheg-Box} v2, both interfaced to \textsc{Herwig++}  for parton shower. The difference computed close to the signal region with enough statistics is used. The PS uncertainty is computed by comparing the the nominal \textsc{Powheg+Pythia6} sample with the PS variation \textsc{Powheg+Herwig++} sample in a region close to the SR but with enough statistics. For ISR/FSR, the dedicated \textsc{radHi} and \textsc{radLo} samples with modified \textsc{hDamp} parameter are compared. The sample with the higher impact on the fit is kept as the uncertainty due to ISR/FSR. Table~\ref{tab:ttbarModeling} shows the numbers provided to the fit for the various \ttbar modeling systematics for the low and high mass selections. Since the uncertainties are computed based on extrapolation from the CRs, these uncertainties are input to the statistical fit as rate uncertainties in the SR only. 

\begin{table}
\centering
\begin{tabular}{l|ccc}
\hline
Source               & Non-resonant &  Low-Mass   & High-Mass   \\\hline\hline 
Parton Shower        & 8.4 &               1.6                &              4.7                 \\\hline
Matrix Element       & 1.5 &               0.9                 &              11.1                 \\\hline
ISR/FSR              & 8.1 &               13.4                &             5.6                 \\\hline
%PDF                  & N/A &               N/A                 &               N/A                 \\\hline
%Scale                & N/A &               N/A                 &               N/A                 \\\hline\hline
\end{tabular}
\caption{Extrapolation uncertainties in percentage from the CR to the SR for all selections,  provided to the fit for the \ttbar modeling systematics.}
\label{tab:ttbarModeling}
\end{table}


\iffalse
An uncertainty on the shape of the $m_{hh}$  for $t\bar{t}$ is derived
comparing  the default Powheg+Herwig++ sample with the distribution obtained
using aMC@NLO+Heriwg++ as alternative generator. Additional systematic
uncertainties are evaluated by comparing the nominal sample showered
with Pythia to one showered with Herwig++. Sample with renormalization
and factorization scales doubled
and halved are also available and used as systematic uncertainty. 
The Samples used for the systematic uncertainties are the following:

\begin{itemize}
\item mc15\_13TeV.410000.PowhegPythiaEvtGen\_P2012\_ttbar\_hdamp172p5\_nonallhad - Nominal
\item mc15\_13TeV.410003.aMcAtNloHerwigppEvtGen\_ttbar\_nonallhad - TTBarMCNLO
\item mc15\_13TeV.410004.PowhegHerwigppEvtGen\_UEEE5\_ttbar\_hdamp172p5\_nonallhad - TTBarHerwig
\end{itemize}
\fi

\subsubsection{Single top uncertainty}
%\textbf{needs review}
Theoretical cross section uncertainties of 5.3\% is assigned to the associated $Wt$ production,  3.9\% to the s-channel and 4.2\% to t-channel single top production.  The dominant production for this analysis is the $Wt$ channel.  The single top modeling systematic uncertainties have been calculated employing the difference between the nominal (DR scheme) and the (available) systematic variation sample (DS scheme) in SR for the $Wt$ channel. The uncertainties are computed to be 12\%, 9\%, and 85\% for non-resonant, low-mass and high-mass analyses respectively. 

%The recommendation is taken from the Top Twiki.{\footnote {\url{https://twiki.cern.ch/twiki/bin/viewauth/AtlasProtected/TopSystematics2015}}} 
%The uncertainties vary across Wt, t, and s channels , and for low mass versus high mass selection. At the smallest it is 3.9\% and at the largest 67\%. To avoid too many nuisance parameters, we have added them in quadrature and now use the following: For Low Mass, 16\% in CR and 34\% in SR. For high mass, 66\% in CR and 69\% in SR.


\subsubsection{$W/Z$+jets modeling uncertainty}
\label{sec:WjetsModeling}
%\textbf{we agreed with the EB to use a more robust procedure for such uncertainties}
Inclusive theoretical uncertainty of 6\% is added in quadrature with 24\% uncertainty for each additional jet. Therefore, in the final SR with 4 or 5 jets, a total uncertainty of 48\% is applied. This procedure has been used in published Top Group analyses~~\cite{Alwall2008}. 

\subsubsection{Diboson uncertainty}
The same procedure as for $W/Z$+jets is followed. 

\subsubsection{QCD uncertainty}
An overall 36\% uncertainty is assigned to the QCD multi-jet background. The systematic uncertainty was calculated following the steps described in Section~\ref{sec:multijet}. 

\subsection{Model uncertainties on the signal}
%\textbf{need to add uncertainties for non resonant, low and high masses on acceptances}
The systematic uncertainties on the modeling of the high mass $H\rightarrow hh$ signal sample have been evaluated checking the acceptance change when spanning the CT10 PDF error set, they amount to 0.4\% while the uncertainties due to missing higher order has been computed varying normalization and factorization scales by a factor two and they amount to 0.6\%.

