%-------------------------------------------------------
\section{ATLAS Detector}
\label{sec:detector}
%-------------------------------------------------------------------------------
The ATLAS detector~\cite{Aad:2008zzm} consists of
four main subsystems: an inner tracking system surrounded by a
superconducting solenoid, electromagnetic and hadronic calorimeters, and a muon spectrometer.
The inner detector provides tracking information from
pixel and silicon microstrip detectors in the pseudorapidity\footnote{ATLAS uses a
right-handed coordinate system with its origin at the nominal
interaction point (IP) in the center of the detector and the $z$-axis
coinciding with the axis of the beam pipe.  The $x$-axis points from
the IP to the center of the LHC ring, and the $y$-axis points
upward. Cylindrical coordinates ($r$,$\phi$) are used in the
transverse plane, $\phi$ being the azimuthal angle around the beam
pipe. The pseudorapidity is defined in terms of the polar angle
$\theta$ as $\eta = - \ln \tan(\theta/2)$.  For the purpose of the
fiducial selection, this is calculated relative to the geometric
center of the detector; otherwise, it is relative to the reconstructed
primary vertex of each event.} range $|\eta|<2.5$ and from a
transition radiation tracker covering $|\eta|<2.0$, all immersed in a 2 T magnetic field
provided by a superconducting solenoid.
The electromagnetic (EM) sampling calorimeter uses lead and liquid-argon (LAr)
and is divided into a barrel region ($|\eta|<1.475$) and an end-cap region
($1.375<|\eta|<3.2$).
Hadron calorimetry is based on two different detector technologies, with
scintillator tiles or LAr as active media, and with either steel, copper, or
tungsten as the absorber material. The calorimeters cover $|\eta|<4.9$.
The muon spectrometer measures the deflection of muon tracks within $|\eta|<2.7$
using multiple layers of high-precision tracking chambers located in a
toroidal field of approximately 0.5 T and 1 T in the central and end-cap
regions of ATLAS, respectively. The muon
spectrometer is also instrumented with separate trigger chambers
covering $|\eta|<2.4$.
