%-------------------------------------------------------------------------------
\section*{Major Changes From Last Version}
\label{sec:changes}
%-------------------------------------------------------------------------------

W.r.t version 0.1, the following had been changed/added:

\begin{enumerate}

\item \w+jets template split by heavy flavor content and corrected using Calibration Factors (CF)
\item Including 1excl. \bt tag channel and perform the fit with 8-channel combination. Corresponding tables and plots updated.
\item All systematics re-evaluated with the new configuration (1excl.+2incl. e+$\mu$ lep+had)
\item CDS comments addressed w.r.t tables, figures, explanations, and consistent notations. 
\item Added appendix summarizing study of 2D correlations between fitted helicity fractions
\item Minuit Output with correlation coefficient plots added to appendix ~\ref{app:minuitOutput}
\end{enumerate}

W.r.t version 0.2, (after 2nd EdBoard meeting) the following had been changed / added:
\begin{enumerate}

\item QCD estimation corrected
\item A bug fixed in TMinuit (background normalization unc. Gaussian priors)
\item All backgrounds in e and $\mu$ channels teated as correlated parameters (except QCD!)
\item All systematics re-evaluated with the corrected templates
\item PDF systematics uncertainty evaluated
\item Mass systematics uncertainty evaluated (using the world average $m_{top}$)
\item $2^{nd}$ round CDS comments addressed
%\item Added appendix summarizing PDF systematic uncertainty evaluation
\end{enumerate}

W.r.t version 0.5, (after 3ed EdBoard meeting) the following had been changed / added:
\begin{enumerate}
\item Almost all CDS comments from the Top Group conveners and EdBoard members are addressed
\item Uncertainty due to the template statistic is evaluated
\item Modified Wtb vertex in single top t-ch has a negligible effect on the fit result (documented in sec.\ref{sec:ew_norm})
\item Using 17\% normalization uncertainty for SingleTop background has negligible effect on the result (a slide is provided in CDS)
\item Tables 8 and 9 are reproduced to show better comparisons
\item Table \ref{tab:DataFit_floatVSfix} added to compare fixed and floating bkg. normalization options
\item bkg. normalization systematics evaluated for fixed bkg. normalization option. Results are summarized in appendix \ref{app:bkgNormSyst}
\item JER systematic evaluated using multiple nuisance parameters (new) in place of single JER parameter as before (old)
\end{enumerate}

%-------------------------------------------------------------------------------
%\section*{To Do List}
%\label{sec:todo}
%-------------------------------------------------------------------------------

%\begin{enumerate}
%\item Applying anti-correlation between w+light and w+HF normalization in the gaussian priors
%\item Taking into account the MC statistics on the templates (?)
%\item Evaluating remaining systematics (lumi ?)
%\item Adding uncertainty band to the control plots -- DONE
%\item Setting limits on anomalous couplings -- DONE
%\item Evaluating effect of modified Wtb vertex in single top t-ch (?) -- done
%\item To consider the MC statistical uncertainty in the fit  -- done
%\item Using 17\% normalization uncertainty for SingleTop background, result will be compared with the current setup -- done
%\item Adding the expected stat. uncertainty (with no LH cut on the leptonic analyzer) to tables 8 and 9 -- done
%\item  ...


%\end{enumerate}
