\begin{acknowledgements}

My PhD years had been blessed years with so many good colleagues and friends. I traveled all around the world, and I worked on the most advanced collider in the world with countless nights of despair and triumph. If I look back, I will remember these years as the most adventurous, full of hopes and dreams, and unforgettable golden years.

And none of these would be possible without my advisor, Prof. KK. From the first day I met him in his office, he guided me through this journey with his continuous supports, patience, wisdom, and fine sense of humor. He trusted in me even when I was losing faith in myself. He truly showed me what a great advisor and scientist should be.

Also, throughout the program, Prof. Kass provided me invaluable advice and supports, and his insightful comments allowed me to see a new perspective on many problems and helped me to refine this dissertation. I would like to extend my special gratitude to the other members of the PhD Committee, Prof. Shigemitsu and Prof. Yang, for their continuous supports and encouragement. They had been the most supportive committee I could ever imagine, and this dissertation wouldn't be complete without their encouragement.

My great colleague and mentor, Dr. Chris Martin had been the most valuable reinforcement in this uphill battle, and I express my sincere gratitude to him. This analysis would be incomplete without his strong supports, dedication, and extraordinary work.

Lastly, I would like to express my deepest gratitude to my parents and sister for their endless love and supports. I still remember the first day I arrived in Columbus with my family, and it was their supports and love that kept me going during the most difficult times. Most importantly, nothing would be possible without God, and I thank him forever.


\end{acknowledgements}

